Convex Surrogates via Polyhedral Losses

### 2019-05-14 neurips-19/poly-embed.tex
comments
Adding examples section

\newcommand{\risk}[1]{\underline{#1}}
\newcommand{\inprod}[2]{\langle #1, #2 \rangle}%\mathrm{int}(#1)}
\newcommand{\inter}[1]{\mathring{#1}}%\mathrm{int}(#1)}
%\newcommand{\expectedv}[3]{\overline{#1}(#2,#3)}
\newcommand{\expectedv}[3]{\E_{Y\sim{#3}} {#1}(#2,Y)}
\newcommand{\toto}{\rightrightarrows}
\newcommand{\strip}{\mathrm{strip}}
\newcommand{\trim}{\mathrm{trim}}
\newcommand{\fplc}{finite-piecewise-linear and convex\xspace} %xspace for use in text
\newcommand{\conv}{\mathrm{conv}}
\newcommand{\ones}{\mathbbm{1}}
\DeclarePairedDelimiter\ceil{\lceil}{\rceil}

@@

In particular, we measure top-$k$ error by 
\begin{align*}
\ell_{top-k}(r,y) &= 
\begin{cases}
0 & r_y = 1 \text{ and } \|r \|_{\infty} \leq k\\
1 & \text{otherwise}
\end{cases}
\end{align*}
Where $r \in 2^n$ can be thought of as a binary vector representing set inclusion and $k \leq n$ is a constant.

Now, for example, consider the surrogate given by Yang and Koyejo~\cite{yang2018consistency}, \jessie{... $\psi_1$ is worked out, but would rather have $\psi_2$.  Working on it.}

>>>>

\newcommand{\risk}[1]{\underline{#1}}
\newcommand{\inprod}[2]{\langle #1, #2 \rangle}%\mathrm{int}(#1)}
\newcommand{\inter}[1]{\mathring{#1}}%\mathrm{int}(#1)}
%\newcommand{\expectedv}[3]{\overline{#1}(#2,#3)}
\newcommand{\expectedv}[3]{\E_{Y\sim{#3}} {#1}(#2,Y)}
\newcommand{\toto}{\rightrightarrows}
\newcommand{\strip}{\mathrm{strip}}
\newcommand{\trim}{\mathrm{trim}}
\newcommand{\fplc}{finite-piecewise-linear and convex\xspace} %xspace for use in text
\newcommand{\conv}{\mathrm{conv}}
\newcommand{\indopp}{\bar{\mathbbm{1}}}
\newcommand{\ones}{\mathbbm{1}}
\DeclarePairedDelimiter\ceil{\lceil}{\rceil}

@@

In particular, we measure top-$k$ error by 
\begin{align}
\ell_{top-k}(r,y) &= 
\begin{cases}
0 & r_y = 1 \text{ and } \|r \|_{\infty} \leq k\\
1 & \text{otherwise}
\end{cases}
\end{align}
Where $r \in 2^n$ can be thought of as a binary vector representing set inclusion and $k \leq n$ is a constant.

Now, for example, consider the surrogate discussed by Lapin et al.~\cite{yang2018consistency}, and Yang and Koyejo~\cite{yang2018consistency}.
Following the numbering of Yang and Koyejo, we call the surrogate $L_2(u,y) := \max\left( \frac{1}{k} \sum_{i=1}^k (u + \indopp(y))_{[i]} - u_y \right) $, where $\indopp(y) = \ones - e_y$.

It can be verified that $\ell_2(r,y) = \begin{cases}
\min\left(\frac{HD(r, e_y)}{k}, 1\right) & s_y = 1 \\
1 + \min \left(\frac{HD(s, \vec{0})}{k}, 1\right) & s_y = 0
\end{cases}$, where $HD(\cdot, \cdot)$ is the Hamming distance between two vectors.

Since we can see that $\ell_2 \neq \ell_{top-k}$, we can then see that $L_2$ is not consistent with respect to $\ell_{top-k}$.
Similarly, given $L_4(u,y) := \max\left(\frac{1}{k} \sum_{i=1}^k (1 + u_{\setminus y})_{[i]} - s_y, 0\right)$, we can actually see that $L_4$ also embeds $\ell_2$.
We will double up on notation and call this discrete loss $\ell_4$ as well, for the sake of matching subscripts of discrete losses to the surrogates that embed them.

So even though the surrogates $L_2$ and $L_4$ are convex, they are not consistent with respect to $\ell_{top-k}$.
This begs the question: what is the relationship between consistency and convexity of a surrogate loss?
Are there instances where only one can be achieved, but not both?
